Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-02 code/rmarkdown/figures.Rmd
+ fix bug with missing species variable being overwritten + assorted figures and tables fixes

p1.hist <- ggplot(aes(R2),
		data=filter(surrogacy.model.summary.DF, Type=='Environmental')) +
	geom_histogram(fill='grey10') +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of environmental', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=-1.375, y=0.95, label='(c)') +
		coord_cartesian(xlim=c(-1.5, 1))

p2.hist <- ggplot(aes(R2),
		data=filter(surrogacy.model.summary.DF, Type=='Geographic')) +
	geom_histogram(fill='grey10') +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of geographic', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'), 
		plot.background=element_rect(fill='transparent')) +
		geom_text(x=-1.375, y=0.95, label='(d)') +
		coord_cartesian(xlim=c(-1.5, 1))

>>>>

p1.hist <- ggplot(aes(R2),
		data=filter(surrogacy.model.summary.DF, Type=='Environmental')) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of environmental', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=0.05, y=0.95, label='(c)') +
		coord_cartesian(xlim=c(0, 1))

p2.hist <- ggplot(aes(R2),
		data=filter(surrogacy.model.summary.DF, Type=='Geographic')) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of geographic', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'), 
		plot.background=element_rect(fill='transparent')) +
		geom_text(x=0.05, y=0.95, label='(d)') +
		coord_cartesian(xlim=c(0, 1))

### 2016-05-02 code/rmarkdown/tables.Rmd
+ fix bug with missing species variable being overwritten + assorted figures and tables fixes

```{r, echo=FALSE}
curr.DF <- correlation.model.summary.DF %>%
	select(-contains('raw')) %>%
	mutate(Environmental.corr.P=pvalString(Environmental.corr.P),
		Geographic.corr.P=pvalString(Geographic.corr.P), blank=NA, Species=gsub('\\ ', '\\n', Species)) %>%
	select(Species:Environmental.corr.P, blank, Geographic.Marginal.R2:Geographic.corr.P) %>%
	format.dataframe 
emphasize.strong.cells(which(curr.DF$Environmental.corr.P < 0.05, arr.ind=TRUE))
emphasize.strong.cells(which(curr.DF$Geographic.corr.P < 0.05, arr.ind=TRUE))
curr.txt=knitr::kable(
	curr.DF,
	digits=2,
	caption='Correlation between surrogate variables and genetic variation. The $R^2$ columns show the proportion of genetic variation explained by surrogates. Specifically, marginal $R^2$ represents the proportion of variation explained by the fixed effects alone. The conditional $R^2$ represents the proportion of variation explained by the fixed and random effects. All $\\chi^2$ tests were based on one degree of freedom. Significant $P$ values ($P$ < 0.05) indicate that surrogate variables correlate with genetic variation.',
	col.names=c('\\textbf{Species}', '\\textbf{Marginal $R^2$}', '\\textbf{Conditional $R^2$}', '\\textbf{$\\chi^2$}', '\\textbf{\\textit{P}}', '', '\\textbf{Marginal $R^2$}', '\\textbf{Conditional $R^2$}', '\\textbf{$\\chi^2$}', '\\textbf{\\textit{P}}'),
	align=rep('c', ncol(curr.DF)),
	format='latex'
) %>% as.character()

>>>>

```{r, echo=FALSE}
curr.DF <- correlation.model.summary.DF %>%
	select(-contains('raw')) %>%
	mutate(Environmental.corr.P=pvalString(Environmental.corr.P),
		Geographic.corr.P=pvalString(Geographic.corr.P), blank='', Species=gsub('\\ ', '\\n', Species)) %>%
	select(Species:Environmental.corr.P, blank, Geographic.Marginal.R2:Geographic.corr.P) %>%
	format.dataframe(omit=c('Environmental.corr.P', 'blank', 'Geographic.corr.P')) 
emphasize.strong.cells(which(curr.DF$Environmental.corr.P < 0.05, arr.ind=TRUE))
emphasize.strong.cells(which(curr.DF$Geographic.corr.P < 0.05, arr.ind=TRUE))
curr.txt=knitr::kable(
	curr.DF,
	digits=2,
	caption='Correlation between surrogate variables and genetic variation. The $R^2$ columns show the proportion of genetic variation explained by surrogates. Specifically, marginal $R^2$ represents the proportion of variation explained by the fixed effects alone. The conditional $R^2$ represents the proportion of variation explained by the fixed and random effects. All $\\chi^2$ tests were based on one degree of freedom. Significant $P$ values ($P$ < 0.05) indicate that surrogate variables correlate with genetic variation.',
	col.names=c('\\textbf{Species}', '\\textbf{Marginal $R^2$}', '\\textbf{Conditional $R^2$}', '\\textbf{$\\chi^2$}', '\\textbf{\\textit{P}}', '', '\\textbf{Marginal $R^2$}', '\\textbf{Conditional $R^2$}', '\\textbf{$\\chi^2$}', '\\textbf{\\textit{P}}'),
	align=rep('c', ncol(curr.DF)),
	format='latex'
) %>% as.character()
